BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Move training section before model section
Comment out default figures

\begin{figure}
  \centering
  \missingfigure[figheight=8cm]{}
  \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
\end{figure}

@@

\begin{table*}
  \centering
  \missingfigure{}
  \caption{This is usually a table. Tables with numbers are generally easier to read than graphs, so prefer when possible.}
  \label{fig:mainres}
\end{table*}

@@

\begin{figure}
  \centering
  \missingfigure{}
  \missingfigure{}
  \missingfigure{}
  \caption{Visualizations of the internals of the system.}
\end{figure}

>>>>

% \begin{figure}
%   \centering
%   \missingfigure[figheight=8cm]{}
%   \caption{\label{fig:diagram} This is a good place to include a diagram showing how your model works. Examples include a graphical model or a neural network block diagram.}
% \end{figure}

@@

% \begin{table*}
%   \centering
%   \missingfigure{}
%   \caption{This is usually a table. Tables with numbers are generally easier to read than graphs, so prefer when possible.}
%   \label{fig:mainres}
% \end{table*}

@@

% \begin{figure}
%   \centering
%   \missingfigure{}
%   \missingfigure{}
%   \missingfigure{}
%   \caption{Visualizations of the internals of the system.}
% \end{figure}
